Solar wind discontinuities spatial evolution

### 2024-01-20 index.qmd
update omni figures
update

>>>>

## Figures

::: {#fig-examples layout-nrow="1"}

![](figures/examples/artemis_id_example)

![](figures/examples/stereo_id_example)

Examples of IDs from ARTEMIS, STEREO, and JUNO

:::

![Near-Earth' solar wind plasma data during JUNO cruise phase](figures/omni_overview){#fig-omni_overview}

[For code, see [noteboook](notebooks/20_omni_overview.ipynb).]{.aside}

![Model validation](figures/model/juno_model_validation_full){#fig-model_validation}

![Effect of the time resolution on the discontinuity properties](figures/ts_effect){#fig-ts_effect}
